---
title: "20181006_ Batch 47_CSE 7302c_SimpleLinearRegression_Activity"
author: "Insofe Instructor"
date: "October 6, 2018"
output:
  html_document: default
  pdf_document: default
---
# Removing the global variables
```{r}
rm(list = ls())
```

# Setting the working directory
```{r}
setwd("I:/DATA-SCIENCE/FACULTY/BATCH-47/Simple-Linear-Regression/Simple-Linear-Regression-master")
```

# Importing the data from the .csv file
```{r}
bigMac_netHrWages_df = read.csv(file = "BigMac-NetHourlyWage.csv" , header = TRUE)
```

# EDA - Exploratory Data Analysis
## 1. Look at the number of rows and columns

```{r}
dim(bigMac_netHrWages_df)
```

## 2.Display the first and last rows
```{r}
head(bigMac_netHrWages_df)
tail(bigMac_netHrWages_df)
```

## 3. Column names
```{r}
colnames(bigMac_netHrWages_df)
```

## 4. Look at the structure of the dataset using the function `str()`
```{r}
str(bigMac_netHrWages_df)
```

## 5. Look at the summary of the dataset using the `summary()` 
```{r}
summary(bigMac_netHrWages_df)
```

## 6. Checking for 'NA' values
```{r}
sum(is.na(bigMac_netHrWages_df))
```

## 7. Renaming the column names
```{r}
colnames(bigMac_netHrWages_df) = c("Country","BigMacPrice","NetHourlyWages")
```

## 8. Summary after renaming the columns 
```{r}
summary(bigMac_netHrWages_df)
```

# Analysing the data
```{r}
plot(bigMac_netHrWages_df$BigMacPrice, bigMac_netHrWages_df$NetHourlyWages)
```

```{r}
cor(bigMac_netHrWages_df$BigMacPrice, bigMac_netHrWages_df$NetHourlyWages)^2
```

# Creating a linear regression model
```{r}
linearRegressionModel = lm(NetHourlyWages~BigMacPrice, data = bigMac_netHrWages_df)
```

# Analysing the linear regression model
```{r}
coefficients(linearRegressionModel)
summary(linearRegressionModel)
```

# Analysis on the following:-
## Linearity of the linearity of the model
## Independence of errors
## Homoscedasticity 
## Normality of errors (Q-Q plot)
```{r}
par(mfrow = c(2,2))
plot(linearRegressionModel)
```

# Model Building

## Train Test Split
```{r}
rows = seq(1,nrow((bigMac_netHrWages_df)))
trainRows = sample(rows,(70*nrow(bigMac_netHrWages_df))/100)
trainData = bigMac_netHrWages_df[trainRows,] 
testData = bigMac_netHrWages_df[-trainRows,]
```

## Checking for skewness
```{r}
library(e1071)
skewness(trainData$BigMacPrice)
trainData$Log10_BigMacPrice = log10(trainData$BigMacPrice)
skewness(trainData$Log10_BigMacPrice)
```

## Creating a linear model with split train data
```{r}
linearRegressionMode2 = lm(NetHourlyWages~Log10_BigMacPrice, data = trainData)
```
 
## Analysis on the model
```{r}
summary(linearRegressionMode2)
par(mfrow = c(2,2))
plot(linearRegressionMode2)
```

## Evaluation
```{r}
library(DMwR)
regr.eval(trainData$NetHourlyWages, linearRegressionMode2$fitted.values)
```

## Prdict the values on test data
```{r}
testData$Log10_BigMacPrice = log10(testData$BigMacPrice)
Pred<-predict(linearRegressionMode2,testData)
```

## Error verification on test data
```{r}
regr.eval(testData$NetHourlyWages, Pred)
```
