---
title: "Cars Data Lin Reg My Trial"
author: "Insofe Instructor"
date: "October 6, 2018"
output:
  html_document: default
  pdf_document: default
---
# Removing the global variables
```{r}

rm(list=ls())

```

# EDA - Exploratory Data Analysis
## 1. Look at the number of rows and columns using dim()
```{r}
dim(cars)
```

## 2.Display the first and last rows
```{r}
head(cars)
tail(cars)
```

## 3. Column names
```{r}
names(cars)
```

## 4. Look at the structure of the dataset using the function `str()`
```{r}
str(cars)
```

## 5. Look at the summary of the dataset using the `summary()` 
```{r}
summary(cars)
```

## 6. Checking for 'NA' values 
```{r}
sum(is.na(cars))
na_count <-sapply(cars, function(y) sum(length(which(is.na(y)))))
na_count
```

## 8. Summary after renaming the columns 
```{r}
summary(cars)
```

# Analysing the data using plot() and cor()
```{r}
plot(cars$dist,cars$speed,main = "Speed vs Dist",xlab = "Speed", ylab = "Dist")
```

```{r}
cor(cars$dist,cars$speed)
```

# Creating a linear regression model
```{r}
cars_model = lm(dist~speed, cars)
```

# Analysing the linear regression model using coefficients() , summary()
```{r}
summary(cars_model)
```
Conclusion:
1. Model is significant - p-val of F stat is < 0.05
2. speed is significant coz - p-val of T test of of speed (beta1) is < 0.05
3. Intercept is significant as - p-val is < 0.05
4. Since its Simple Lin Reg R squared has to be checked - speed explains 65.11% of variance of dist

# Line of Best Fit
```{r}
plot(cars$speed,cars$dist,xlab = "Speed", ylab = "Dist", col = "red",lwd = 2, main = "Best Fit Line")
abline(cars_model,col="blue",lty=1,lwd=2)
grid(10,10,lwd=1)
```


# Analysis on the following:-
## Linearity of the linearity of the model
## Independence of errors
## Homoscedasticity 
## Normality of errors (Q-Q plot)
```{r}
par(mfrow = c(2,2)) # par - set the size of each plot
plot(cars_model)
```

Conclusion:
Residual Plot: 
 - heteroscadastic

QQ plot
 - Visually no pattern and close to 45 degree line, so errors are normally distributed

Cooks Dist
 - 1 influencial point

# #################################################################################################### #


# Model Building

## Train Test Split 70:30 split
```{r}
set.seed(800)

#train_rows = sample(x = 1:nrow(big_mac),size = 0.7*nrow(big_mac))

rows = seq(1,nrow(cars))
train_rows = sample(rows,(70*nrow(cars))/100)

train_data = cars[train_rows,]
test_data = cars[-train_rows,]

summary(train_data)
summary(test_data)

str(train_data)
str(test_data)

dim(train_data)
dim(test_data)
```

## Checking for skewness using skewness()
```{r}
library(e1071)

skewness(train_data$speed)
skewness(train_data$dist)
```
Both are not much skewed



## Creating a linear model with splitted train data
```{r}
trained_model = lm(dist~speed,train_data)

```
 
## Analysis on the model using sumary()
```{r}
summary(trained_model)
```

Conclusion:
1. speed is a significant variable since p-val(T-test) < 0.05
2. speed explains 61.23% of variance
3. the model is significant p-val(F-stat) < 0.05



## Evaluation model on train data using regr.eval()
```{r}
library(DMwR)
regr.eval(train_data$dist, trained_model$fitted.values)
```

## Predict the values on test data
```{r}
dim(test_data)
head(test_data,10)
predicted_test_dist <- predict(trained_model, test_data)
predicted_test_dist
```

## Error verification on test data
```{r}
regr.eval(test_data$dist, predicted_test_dist)
```
