---
title: '- ALAGAPPAN_RAMANATHAN_CUTe01_7212c.Rmd'
author: "ALAGAPPAN RAMANATHAN"
date: "7 July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
#1. The dataset "go_tracks.csv" contains various information collected by a 'goTracks
#App' based on GPS information. The details of the dataset is provided in the text
#file "Data_Description.txt".
#a. Import the 'go_tracks.'csv' file into R. (1 mark)
setwd("C:\\notes r studio\\cute exam 1")
go_tracks=read.table(file="go_tracks.csv",header = T,sep = ",",na.strings= {c("NA","?")})

#b. Look at the structure and summary of the datasets. Observe the data and
#report your findings as comments in your R file. (2 marks)
str(go_tracks)#to get the structure of the data set which shows the totals observations and columns
#go tracks DATA SETS has all numerical variables and one categorical column called linha with 23 levels and where the ratings of the buses are should be in categorical but which is not in this case
summary(go_tracks)#its a generic function which gives whole stats information about the data 
#summary of this data sets has total of 19missing values I.E iths has 19 NA values,in time coloumn MAx values is very higher from the 3rd quartile and that may be a outlier and even in spped column its has a huge difference btwn a 3rdquartile and the max value and column linha has a mode as  carro with 33 repetition



```
#c. Convert the attributes into appropriate data types. (2 marks)
```{r}
go_tracks$rating=as.factor(go_tracks$rating)
#go_tracks$rating= factor(go_tracks$rating, order = TRUE, levels = c("3"," 2", "1"))
go_tracks$rating_bus =as.factor(go_tracks$rating_bus)
go_tracks$rating_weather=as.factor(go_tracks$rating_weather)
go_tracks$car_or_bus =as.factor(go_tracks$car_or_bus)
go_tracks$rating=as.factor(go_tracks$rating)
go_tracks$id_android =as.factor(go_tracks$id_android)
str(go_tracks)

go_tracks$speed[1]


```
#d. Impute the na values, "?" should be treated as na. (1 mark).
```{r}
#go_tracks=read.table(file="go_tracks.csv",header = T,sep = ",",na.strings= {c("NA","?")})
#the line of code which i used to read the will treat "?" as NA values"
library(DMwR)
imputed_gotracks=centralImputation(go_tracks)
sum(is.na(imputed_gotracks))# NA values are imputed using central imputation function which is used to fill the columns wNA values with statistic centrality
```
#ee. Write a user-defined function which takes in a numeric attribute and returns
the range of that attribute. (Do not use any inbuilt functions like range, max,
min or apply functions etc).
Apply the function you made and find the range of the following attributes in
this dataset - 'speed', 'time' and 'distance'. (5 marks)
```{r}
rng=function(x)
{
  a=sort(x,decreasing = F)# i sorted the data in accending order sothat the 1st value of the data will be minimum and last will be max so that it will be easy to extraxt and find the diffrence
  maxx=a[NROW(x)]#print the max value i.e last value in the data set
  minn=a[1]#print 1st value i.e min values in data set
  rngg=maxx-minn
  print("MAX VALUE IS")
  print(maxx)
  print("MIN VALUE IS")
  print(minn)
  print("RANGE IS")
  print(rngg)
  }

rng(imputed_gotracks$speed)
rng(imputed_gotracks$distance)
rng(imputed_gotracks$time)
```
f. Use any of the apply functions in R and find the mean of the attributes -
'speed' and 'distance'. (1 mark)
```{r}
str(imputed_gotracks)
lapply(imputed_gotracks[3],mean)
sapply(imputed_gotracks[3],mean)
#or

lapply(imputed_gotracks[5],mean)
sapply(imputed_gotracks[5],mean)
#or

apply(imputed_gotracks[3:5],2,mean)

#both sapply and lapply functions can be used and where l apply returs list and sapply returns vector and in apply function 2 means its column wise
```
#g. Use a 'for loop' to loop through the values in the attribute 'distance' and find
the maximum distance travelled. You should not use the inbuilt function for
this. (2 marks)
```{r}
sum=0
a=0
for(w in 1:length(imputed_gotracks$distance))
{
if(((imputed_gotracks$distance[w]>imputed_gotracks$distance[w+1])==T)&&(imputed_gotracks$distance[w]>a)==T)
  { 
    a=imputed_gotracks$distance[1]
  }
  else{
  
    if(imputed_gotracks$distance[w+1]>a)
  {
    a=imputed_gotracks$distance[w+1]
  }
}}
print(a)
```
#h. Access the rows 1-10 for the columns - 'speed', 'time', 'distance'. Save the
result into a new df called GPS_df. Is it a numeric or a character df? Find the
sum of the columns of the newly created df and report your results. (2 marks)
```{r}
gps_df=imputed_gotracks[1:10,3:5] #saving the results of 1st 10 columns in new dataset
class(gps_df$speed)
class(gps_df$time)
class(gps_df$distance)
#its numeric
colSums(gps_df)
```
i. Calculate the Variance for all the numeric columns in GPS_df. (1 mark)
```{r}
var(gps_df) 
var(gps_df[,1:3])
# as all gthe columns are numeric var function is used to find the variance for all the data set
```
j. Standardize the GPS_df columns. (1 mark)
```{r}
library(vegan) #this library is used to use function decostand which is used to standardize
gps_df[,1:3]=decostand(x=gps_df[,1:3],method = "range",MARGIN = 2)#its is standardized in tye method range
```
k. Find the average speed when the traffic rating given is 'bad' and the weather
is 'raining'. (2 marks)
```{r}
summary(imputed_gotracks)
tapply(go_tracks$speed,go_tracks$rating_weather,mean)
tapply(imputed_gotracks$speed,imputed_gotracks$rating,mean)
tapply(imputed_gotracks$speed,imputed_gotracks$rating_weather,mean)
#as level 1 is gives as raining day and 1 has a average speed of 8.380064 and 8.380064 divided by average number of bad rating 17 so
g=8.380064/17#17 is no of bad ratings
g
#0.4929449 is the ans
```
