---
title: "Amith_Prasad_CUTe01_7212c"
author: "Amith Prasad"
date: "9/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# a. Import the ???go_tracks.???csv??? file into R.
```{r cars}
rm(list=ls(all=TRUE)) #clears the environment

getwd()
setwd("/Users/amithprasad/repos/insofe_data_sc/CUTe_CSE_7212c _Amith_Prasad") #setting the working directory

#Importing csv
data<-read.csv("dataset/go_tracks.csv",header=T,na.strings = c(NA,"?"))
head(data)

```
# b. Look at the structure and summary of the datasets. Observe the data and
# report your findings as comments in your R file.
```{r}
str(data)
```

```{r}
summary(data)
```

```{r}
dim(data)
```
```{r}
unique(data$rating_weather)
```

```{r}
unique(data$linha)
```

```{r}
sum(is.na(data))
```

```{r}
# There are 163 rows and 10 columns
# Looking at the data the 
# Numberical fields are:
# speed
# time
# distance
# 
# Categorical Fields are:
# id
# id_android
# rating
# rating_bus
# rating_weather
# car_or_bus
# linha

# rating has 5 levels
# rating_bus has 5 levels
# rating_weather has 3 levels
# car_or_bus hash 3 levels
# linha has 23 levels

# there are 19 NAs(missing values) in speed, time, distance, rating, rating_bus, rating_weather and car_or_bus will have to impute them
```

#c. Convert the attributes into appropriate data types
```{r}
num_data = subset(data,select=c(speed,time,distance))
cat_data = subset(data,select=-c(speed,time,distance))
```

```{r}
# converting to factor type for categorical data
cat_data = data.frame(
  apply(cat_data,2,function(x){as.factor(x)}))
str(cat_data)
```

```{r}
# converting to factor type for categorical data
num_data = data.frame(
  apply(num_data,2,function(x){as.numeric(x)}))
str(num_data)
```

# d. Impute the na values, ??????? should be treated as na.  
```{r}
# have converted ? to NA while reading the file
# linha column has almost half the values empty so imputing the column will result in too much synthetic data
library(DMwR)
manyNAs(data, 0.1) 

# numeric data imputation
num_data_imputed = centralImputation(num_data) #Cenral Imputation

# numeric data imputation
cat_data_imputed = centralImputation(cat_data) #Cenral Imputation

```

```{r}
summary(num_data_imputed)
str(num_data_imputed)
```

# e. Write a user-defined function which takes in a numeric attribute and returns
# the range of that attribute. (Do not use any inbuilt functions like range, max, min or apply functions etc).
# Apply the function you made and find the range of the following attributes in this dataset - ???speed???, ???time??? and ???distance???.
```{r}

custom_range = function(x){
  sorted_x = sort(x,decreasing = F)
  min = sorted_x[1]
  max = sorted_x[NROW(sorted_x)]
  print("min: ")
  print(min)
  print("max: ")
  print(max)
  print("range: ")
  print(max-min)
}

custom_range(num_data_imputed$speed)
custom_range(num_data_imputed$time)
custom_range(num_data_imputed$distance)
```

# f. Use any of the apply functions in R and find the mean of the attributes - ???speed??? and ???distance???.

```{r}
mean(num_data_imputed$speed)
mean(num_data_imputed$distance)

apply(num_data_imputed[1],2,mean)
apply(num_data_imputed[3],2,mean)
```


# g. Use a ???for loop??? to loop through the values in the attribute ???distance??? and find the maximum distance travelled. You should not use the inbuilt function for this.

```{r}
max = 0
for (x in num_data_imputed$distance) {
  if (x > max){
    max = x
  }
}
print(max)
```
# h. Access the rows 1-10 for the columns - ???speed???, ???time???, ???distance???. Save the result into a new df called GPS_df. Is it a numeric or a character df? Find the sum of the columns of the newly created df and report your results.

```{r}
GPS_df=num_data_imputed[1:10,]
class(GPS_df$speed)
class(GPS_df$time)
class(GPS_df$distance)
# its numeric dataframe
colSums(GPS_df)
```

# i. Calculate the Variance for all the numeric columns in GPS_df.
```{r}
# variance
var(GPS_df)
```

# j. Standardize the GPS_df columns.
```{r}
str(num_data_imputed)
# standardize
library(vegan)
num_data_imputed_std = decostand(num_data_imputed,"standardize") 
str(num_data_imputed_std)
```

# k. Find the average speed when the traffic rating given is ???bad??? and the weather
# is ???raining???.
```{r}
# merged the data
final_data = data.frame(cat_data_imputed,num_data_imputed)
final_data
head(final_data)
str(final_data)


str(final_data$rating)
final_data$rating_weather
final_data[1,1]
custom_data = final_data[as.numeric(final_data$rating) == 1 & as.numeric(final_data$rating_weather) == 2,]
custom_data
mean(custom_data$speed)
```



