---
title: "Simple Linear Regression"
author: "INSOFE Lab"
date: "02nd Sep 2018"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes

---

**NOTE** Before starting, please remember to clear your environment, you can do that by running the following code chunk

```{r}

rm(list = ls(all=TRUE))

```

# Agenda 

* Reading & Understanding the Data

* Data Description

* Basic Stats

* Covariance and Correlation

* Linear Regression

* Plotting the data

* Summary Statistics

* Basic assessment of the model


# Reading & Understanding the Data

Read the cars dataset which comes in built in R.

```{r}

data(cars);
attach(cars);


```

# Data Description
Basic description about the dataset

```{r}

dim(cars); #Size of data
names(cars); #names of attributes in the cars dataframe
summary(cars);
head(cars);

```

We take the speed to be the independent variable (based on domain knowledge) and stopping distance as the dependent variable

# Basic Stats
Compute basic statistics


```{r}

print("Mean and standard deviation of speed : ");
print(toString(mean(speed)));
print(toString(sd(speed)));

print("Mean and standard deviation of dist : ");
print(toString(mean(dist)));
print(toString(sd(dist)));


```

# Covariance and Correlation

*Compute the covariance and correlation between dependent and independent variables
*Verify that these values match the covariance and correlation computed using Excel.
*You are encouraged to ask other questions (not just about prices of cars) and answer them using the dataset below.

```{r}

covariance_speed_dist = cov(speed,dist);
correlation_speed_dist = cor(speed,dist);

# verifying the formula
r= covariance_speed_dist/(sd(speed)*sd(dist))
r

print("Covariance between speed and dist = ");
print(toString(covariance_speed_dist));

print("Correlation between speed and dist = ");
print(toString(correlation_speed_dist));

```

# Linear Regression
'lm' function is used for Linear Regression

```{r}
linefit = lm(dist~speed,data=cars);
linefit

linefit_trial = lm(dist~.,data=cars);
linefit_trial
```

# Plotting the data

* Plot Distance vs Speed.

* Superimpose the Predicted line over original data.


```{r}

plot(speed,dist,xlab="Speed (mph)",ylab="Stopping distance (ft)",main="Scatter plot of stopping distance vs speed for cars data\n + best fit line superimposed");
abline(linefit,col="steelblue",lty=1,lwd=4); 
grid(10,10,lwd=2);

```

# Summary Statistics
Read off key outputs of the fitted model using the summary function

```{r}

summary(linefit);

```

#Basic assessment of the model
Is the model significant?
Are the individual coefficients significant?
What is the RSquared value?
































