---
title: "Arima_Step_by_Step"
author: "Insofe Instructor"
date: "September 22, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r}
rm(list=ls(all=TRUE))
library(forecast)
```

```{r}
setwd("I:/DATA-SCIENCE/FACULTY/BATCH-47/CSE7302c-Statistics and Probability in Decision Modeling/TimeSeries/20180922_Batch47_CSE7302c_Time_Series_LabActivity")
miles = read.csv("us-air-carrier-traffic-statistic.csv")
miles
```
#ARIMA
##Step-by-step ARIMA model building
## Step 1: Plot timeseries (in terms of ARIMA, it is an ARIMA(0,0,0))
```{r}
milestimeseries <- ts(miles, frequency = 12, start = c(1996,1))
milestimeseries
par(mfrow = c(1, 1))
plot(milestimeseries)
```

## Step 2: Plot ACF and PACF to get preliminary understanding of the process
```{r}
par(mfrow = c(1, 2))
acf(milestimeseries)
pacf(milestimeseries)
```

## Step 3: The suspension bridge pattern in ACF suggests both nonstationarity and strong seasonality.  Perform a non-seasonal difference to give an ARIMA(0,1,0) model
```{r}
par(mfrow = c(1, 1))
milestimeseriesdiff1 <- diff(milestimeseries, differences = 1)
milestimeseriesdiff1
plot(milestimeseriesdiff1)
```

## Step 4: Check ACF and PACF to explore remaining dependencies
```{r}
par(mfrow = c(1, 2))
acf(milestimeseriesdiff1)
pacf(milestimeseriesdiff1)
```

## Step 5: The differenced series looks stationary but has strong seasonal lags. Perform a seasonal differencing on the original time series (ARIMA(0,0,0)(0,1,0)12)
```{r}
par(mfrow = c(1, 1))
milestimeseriesseasonaldiff1 <- diff(milestimeseries, lag = 12, differences=1)
milestimeseriesseasonaldiff1
plot(milestimeseriesseasonaldiff1)
```

## Step 6: Check ACF and PACF for seasonally differenced data to explore remaining dependencies
```{r}
par(mfrow = c(1, 2))
acf(milestimeseriesseasonaldiff1)
pacf(milestimeseriesseasonaldiff1)
```

## Step 7: Strong positive autocorrelation indicates need for either an AR component or a non-seasonal differencing.  Perform a non-seasonal differencing. ARIMA(0,1,0)(0,1,0)12
```{r}
par(mfrow = c(1, 1))
milestimeseriesSeasNoSeasdiff1 <- 
  diff(milestimeseriesseasonaldiff1, differences=1)
milestimeseriesSeasNoSeasdiff1
plot(milestimeseriesSeasNoSeasdiff1)
```

## Step 8: Check ACF and PACF to explore remaining dependencies
```{r}
par(mfrow = c(1, 2))
acf(milestimeseriesSeasNoSeasdiff1)
pacf(milestimeseriesSeasNoSeasdiff1)
```

## Step 9: ACF and PACF show significant lag-1, which then cutoff, requiring an AR(1) and an MA(1) term.  Also, the significant lag at the seasonal period is negative, requiring a SeasonalMA(1) term
```{r}
milesArima1 <- Arima(milestimeseries, order = c(1,1,1),
                     seasonal = c(0,1,1), include.drift = FALSE)
milesArima1

```

## Step 10: Check residuals to ensure they are white noise
```{r}
par(mfrow = c(1, 2))
acf(milesArima1$residuals, lag.max = 24)
pacf(milesArima1$residuals, lag.max = 24)
Box.test(milesArima1$residuals, lag=24, type="Ljung-Box")
```

## Step 11: Start forecasting
```{r}
par(mfrow = c(1, 1))
milestimeseriesforecastsArima1 <- forecast(milesArima1, 
                                                 h=36)
plot(milestimeseriesforecastsArima1)
milestimeseriesforecastsArima1
```

# Auto ARIMA - Automated functions are available
```{r}
milesAutoArima <- auto.arima(milestimeseries,ic='aic')
milesAutoArima
milestimeseriesforecastsAutoArima <- forecast(milesAutoArima, 
                                                    h=36)
plot(milestimeseriesforecastsAutoArima)
milestimeseriesforecastsAutoArima
```