---
title: "ADABoost Methodology"
author: "Insofe Lab - Batch 47"
date: "4th Nov 2018"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
---

#Clearing the Environment

```{r}
  
  rm(list=ls(all.names=TRUE))

```


# the Univ_bank dataset has 14 variables and 5000 records. Use loan as target variable. 

# read the dataset into R

```{r}

  # setwd("")
  U_Bank <-read.csv(file="UniversalBank.csv",header=T,sep=",",fill=T)

```


# drop unnecessary the attributes (ID & ZIP Code)

```{r}

  str(U_Bank)
  U_Bank <-U_Bank[,-c(1,5)]
  str(U_Bank)

```


# subset data into numeric and categorical

```{r}

  U_Bank_Num <- subset(x = U_Bank, select = c(Age, Experience, Income, Family, CCAvg, Mortgage))
  U_Bank_Cat <- subset(x = U_Bank, select = -c(Age, Experience, Income, Family, CCAvg, Mortgage))

```


# convert categorical attributes into factors

```{r}
  
  U_Bank_Cat <- data.frame(apply(X = U_Bank_Cat, MARGIN = 2, FUN = as.factor))

```


# dummify all categorical attributes (except "Personal.Loan")

```{r}
  
  library(dummies)
  data_cat_dummy <-dummy.data.frame(U_Bank_Cat[,-c(2)])
  str(data_cat_dummy)
  
```


# convert numerical attributes into numerics

```{r}
  
  U_Bank_Num <- data.frame(apply(X = U_Bank_Num, MARGIN = 2, FUN = as.character))
  U_Bank_Num <- data.frame(apply(X = U_Bank_Num, MARGIN = 2, FUN = as.numeric))


  # Combining categorical and numerical datasets 
  data_combine <- cbind(data_cat_dummy, U_Bank_Num)
  str(data_combine)
  
  # Standardize the combined datset
  library(vegan)
  data_std <- decostand(x = data_combine,method = "range")
  str(data_std)
  
  # Add "Personal.Loan" back into the dataset
  data_final <- cbind(data_std,U_Bank_Cat$Personal.Loan)
  str(data_final)
  colnames(data_final)[18] <-c("Personal.Loan")
  
```

#Data Sampling and Model Building
  
```{r}

  # Split data into train and test
  rows <- seq(from = 1, to = nrow(data_final), by = 1)
  set.seed(2020)
  trainrows <- sample(x = rows, size = nrow(data_final) * 0.7)
  trainR <- data_final[trainrows,] #all rows in trainrows & all columns of parent dataset
  testR <- data_final[-trainrows,]
  
  # build the classification model using Adaboost
  library(ada) 
  x = subset(trainR, select = -Personal.Loan) 
  y = as.factor(trainR$Personal.Loan) 
  a = subset(testR, select = -Personal.Loan) 
  b = as.factor(testR$Personal.Loan) 

  model = ada(x, y, iter=20, loss="logistic") # 20 Iterations 
  model
  
  # predict the values using model on test data sets. 
  pred = predict(model, a);pred 
  
  # calculate accuracy 
  result <- table(pred, b);result # 0(-ve) and 1(+ve)
  accuracy <- sum(diag(result))/sum(result)*100;accuracy
  
  # experiment with different number of iterations to get the best results

```


