---
title: 'Logistic Reg : Parkinsons Classification'
output: html_document
---

```{r}
rm(list = ls(all=TRUE))
```

```{r}
file_path = "/Users/amith.prasad/Documents/parkinsons_data.csv"
parkinson_data = read.delim(file_path,sep=',')
```

```{r}
head(parkinson_data)
tail(parkinson_data)
```
```{r}
summary(parkinson_data)
str(parkinson_data)
```

# check for NAs
```{r}
sum(is.na(parkinson_data))
```

# No NAs - so imputation needed

# normalize
```{r}
class(parkinson_data)
#removing status column
parkinson_data_x = subset(parkinson_data,select=-c(status))

#normalizing
parkinson_data_norm_x = scale(parkinson_data_x)

# putting back status column
parkinson_data_norm_x = as.data.frame(parkinson_data_norm_x)
class(parkinson_data_norm_x)
parkinson_data_norm = cbind(parkinson_data_norm_x,parkinson_data$status)
colnames(parkinson_data_norm)[23] = "status"
str(parkinson_data_norm)
```

# train test split
# make sure status is equally(70:30) split in train and test
```{r}
library(caret)
set.seed(123)

train_rows <- createDataPartition(parkinson_data_norm$status, p = 0.7, list = F)
train_data <- parkinson_data_norm[train_rows, ]
test_data <- parkinson_data_norm[-train_rows, ]

```

```{r}
str(train_data)
dim(train_data)
```

```{r}
str(test_data)
dim(test_data)
```

```{r}
log_reg <- glm(status~., data = train_data, family = binomial)
```
```{r}
summary(log_reg)
```

# AIC lower is better
```{r}
Devaince_residuals = residuals(log_reg, "deviance")
summary(Devaince_residuals)
```

```{r}
logLik(log_reg)
```

```{r}
prob_train <- predict(log_reg, type = "response")
```

```{r}
library(ROCR)

pred <- prediction(prob_train, train_data$status)

```

```{r}
perf <- performance(pred, measure="tpr", x.measure="fpr")
plot(perf, col=rainbow(10), colorize=T, print.cutoffs.at=seq(0,1,0.05))
```

```{r}
perf_auc <- performance(pred, measure="auc")

auc <- perf_auc@y.values[[1]]
print(auc)
```

```{r}
prob_test <- predict(log_reg, test_data, type = "response")
preds_test <- ifelse(prob_test > 0.1, "yes", "no")

```

```{r}
test_data_labs <- test_data$status
conf_matrix <- table(test_data_labs, preds_test)
print(conf_matrix)

```

```{r}
library(caret)

str(preds_test)
unique(preds_test)
preds_test_factor = factor(preds_test,labels=c("Normal","Parkinson's"))

str(preds_test_factor)
str(test_data$status)
preds_test_factor
test_data$status
confusionMatrix(preds_test_factor, test_data$status, positive = "Parkinson's")
```

```{r}
library(MASS)

step_aic = stepAIC(log_reg,direction='both')
```

```{r}
summary(step_aic)
```

```{r}
library(car)

vif(step_aic)
```


# performing prediction on step aic

# AIC lower is better
```{r}
Devaince_residuals = residuals(step_aic, "deviance")
summary(Devaince_residuals)
```

```{r}
logLik(step_aic)
```

```{r}
prob_train <- predict(step_aic, type = "response")
```

```{r}
library(ROCR)

pred <- prediction(prob_train, train_data$status)

```

```{r}
perf <- performance(pred, measure="tpr", x.measure="fpr")
plot(perf, col=rainbow(10), colorize=T, print.cutoffs.at=seq(0,1,0.05))
```

```{r}
perf_auc <- performance(pred, measure="auc")

auc <- perf_auc@y.values[[1]]
print(auc)
```

```{r}
prob_test <- predict(step_aic, test_data, type = "response")
preds_test <- ifelse(prob_test > 0.1, "yes", "no")

```

```{r}
test_data_labs <- test_data$status
conf_matrix <- table(test_data_labs, preds_test)
print(conf_matrix)
```

```{r}
library(caret)

str(preds_test)
unique(preds_test)
preds_test_factor = factor(preds_test,labels=c("Normal","Parkinson's"))

str(preds_test_factor)
str(test_data$status)
preds_test_factor
test_data$status
confusionMatrix(preds_test_factor, test_data$status, positive = "Parkinson's")
```

# in this data since Parkinson's is yes
# So Reduce False -ve, so increase Recall = true +ve / actual +ve

# change the threshold so as to increase recall / sensitivity = with threshold at 0.1 sensitivity is 1. so that is the best result.


