---
title: "MiTH_20181201"
author: "Amith Prasad"
date: "12/1/2018"
output: html_document
---

```{r}
rm(list=ls(all=TRUE))
```

```{r}
setwd(dir = "/Users/amithprasad/repos/insofe_data_sc/EXAMS/MiTH")
```

```{r}
# actual claim amount range
train = read.csv("Train-1542969243754.csv",header=T,na.strings = c(NA,"?"," ","",".","NA")) 

# details of claim
train_claim_details = read.csv("Train_ClaimDetails-1542969243754.csv",header=T,na.strings = c(NA,"?"," ","",".","NA"))

# contains details of policy holder
train_demographics = read.csv("Train_Policy_Demographics-1542969243754.csv",header=T,na.strings = c(NA,"?"," ","",".","NA"))
```

```{r}
test = read.csv("Test-1542969243754 (1).csv",header=T,na.strings = c(NA,"?"," ","",".","NA"))

test_claim_details = read.csv("Test_ClaimDetails-1542969243754.csv",header=T,na.strings = c(NA,"?"," ","",".","NA"))

test_demographics = read.csv("Test_Policy_Demographics-1542969243754.csv",header=T,na.strings = c(NA,"?"," ","",".","NA"))
```

```{r}
str(train)
str(train_claim_details)
str(train_demographics)
```


```{r}
str(test)
str(test_claim_details)
str(test_demographics)
```

# combining the data from the 3 files and removing claim_id from the other 2 files as its redundant
```{r}
train_claim_details = subset(train_claim_details, select = -c(ClaimID))
train_demographics = subset(train_demographics, select = -c(ClaimID))

test_claim_details = subset(test_claim_details, select = -c(ClaimID))
test_demographics = subset(test_demographics, select = -c(ClaimID))
```

```{r}
complete_train = data.frame(train,train_claim_details,train_demographics)
str(complete_train)
```


```{r}
complete_test = data.frame(test,test_claim_details,test_demographics)
str(complete_test)

```

# frequency distribution of target variable
```{r}
table(complete_train$ClaimSize)
barplot(t(table(complete_train$ClaimSize)))
```

# there seems to be a class imbalance
# lessthan100K is twice as much as the other 2 classes

# total NA values
```{r}
sum(is.na(complete_train))

```


```{r}
library(DataExplorer)
create_report(complete_train)
```

```{r}
dim(complete_train)
```

```{r}
str(complete_train)
```

# columnwise distribution of NA values
```{r}
na_count <-sapply(complete_train, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count
```


# SystemicPoisoning_other - 14389 NAs - 99.8% of values are NA
# Falls - 12403 NAs - 86% of values are NA
# Match_Multiclaimant_multiInterestedparties_claim - 11662 NAs - 80.89% of values are NAs

# all the columns having atleast 80% or more values as NAs, so dropping them would be a better option as they are providing no useful info
```{r}
# complete_train = complete_train[, -which(colMeans(is.na(complete_train)) > 0.8)]
# str(complete_train)
# 
# complete_test = complete_test[, -which(colMeans(is.na(complete_test)) > 0.8)]
# str(complete_test)
```

# on running different models with dropping columns having more than 80% NA values the accuracy was hovering around 68%
# but keeping all the columns resulted in an accuracy hovering around 73%
# so decided to keep all the columns intact as without removing any column the accuracy is increasing by 5-6%

```{r}
sum(is.na(complete_train))
```

# there are 5 columns which have 30% to 70% NA values
# since this is insurance data imputing doesn't make sense
# so leaving the rest of the data as it is and renaming NA to 'Dont Know'
# columnwise distribution of NA values
```{r}
na_count <-sapply(complete_train, function(y) sum(length(which(is.na(y)))))
na_count <- data.frame(na_count)
na_count
```


# binning NAs to dont_know
```{r}
#library(lubridate)

str(complete_train)

complete_train$Work_related_injury_status = as.character(complete_train$Work_related_injury_status)
complete_train$Work_related_injury_status[is.na(complete_train$Work_related_injury_status)] = "Dont_Know"
complete_train$Work_related_injury_status = as.factor(complete_train$Work_related_injury_status)
table(complete_train$Work_related_injury_status)

complete_train$MultipleInjuries = as.character(complete_train$MultipleInjuries)
complete_train$MultipleInjuries[is.na(complete_train$MultipleInjuries)] = "Dont_Know"
complete_train$MultipleInjuries = as.factor(complete_train$MultipleInjuries)
table(complete_train$MultipleInjuries)

complete_train$BackInjury = as.character(complete_train$BackInjury)
complete_train$BackInjury[is.na(complete_train$BackInjury)] = "Dont_Know"
complete_train$BackInjury = as.factor(complete_train$BackInjury)
table(complete_train$BackInjury)

complete_train$OtherInjuries = as.character(complete_train$OtherInjuries)
complete_train$OtherInjuries[is.na(complete_train$OtherInjuries)] = "Dont_Know"
complete_train$OtherInjuries = as.factor(complete_train$OtherInjuries)
table(complete_train$OtherInjuries)

complete_train$OtherMotorVehicle = as.character(complete_train$OtherMotorVehicle)
complete_train$OtherMotorVehicle[is.na(complete_train$OtherMotorVehicle)] = "Dont_Know"
complete_train$OtherMotorVehicle = as.factor(complete_train$OtherMotorVehicle)
table(complete_train$OtherMotorVehicle)

complete_train$Age_Injured = complete_train$Age_Injured/100

```

```{r}
complete_test$Work_related_injury_status = as.character(complete_test$Work_related_injury_status)
complete_test$Work_related_injury_status[is.na(complete_test$Work_related_injury_status)] = "Dont_Know"
complete_test$Work_related_injury_status = as.factor(complete_test$Work_related_injury_status)
table(complete_test$Work_related_injury_status)

complete_test$MultipleInjuries = as.character(complete_test$MultipleInjuries)
complete_test$MultipleInjuries[is.na(complete_test$MultipleInjuries)] = "Dont_Know"
complete_test$MultipleInjuries = as.factor(complete_test$MultipleInjuries)
table(complete_test$MultipleInjuries)

complete_test$BackInjury = as.character(complete_test$BackInjury)
complete_test$BackInjury[is.na(complete_test$BackInjury)] = "Dont_Know"
complete_test$BackInjury = as.factor(complete_test$BackInjury)
table(complete_test$BackInjury)

complete_test$OtherInjuries = as.character(complete_test$OtherInjuries)
complete_test$OtherInjuries[is.na(complete_test$OtherInjuries)] = "Dont_Know"
complete_test$OtherInjuries = as.factor(complete_test$OtherInjuries)
table(complete_test$OtherInjuries)

complete_test$OtherMotorVehicle = as.character(complete_test$OtherMotorVehicle)
complete_test$OtherMotorVehicle[is.na(complete_test$OtherMotorVehicle)] = "Dont_Know"
complete_test$OtherMotorVehicle = as.factor(complete_test$OtherMotorVehicle)
table(complete_test$OtherMotorVehicle)

complete_test$Age_Injured = complete_test$Age_Injured/100

```

# converting numerical to numeric
```{r}
train_num_data = subset(complete_train,select=c(Age_Injured,PrimaFacie_percentagefault_injured,PrimaFacie_percentagefault_insured,PrimaFacie_percentagefault_otherinsured,PrimaFacie_percentagefault_uninsured,BusinessClass,Perperson_Policylimit,PerOccurrence_PolicyLimit,CombinedSingleLimit, PolicyLimitPerInjury))

train_cat_data = subset(complete_train,select=-c(Age_Injured,PrimaFacie_percentagefault_injured,PrimaFacie_percentagefault_insured,PrimaFacie_percentagefault_otherinsured,PrimaFacie_percentagefault_uninsured,BusinessClass,Perperson_Policylimit,PerOccurrence_PolicyLimit,CombinedSingleLimit, PolicyLimitPerInjury))

test_num_data = subset(complete_test,select=c(Age_Injured,PrimaFacie_percentagefault_injured,PrimaFacie_percentagefault_insured,PrimaFacie_percentagefault_otherinsured,PrimaFacie_percentagefault_uninsured,BusinessClass,Perperson_Policylimit,PerOccurrence_PolicyLimit,CombinedSingleLimit, PolicyLimitPerInjury))

test_cat_data = subset(complete_test,select=-c(Age_Injured,PrimaFacie_percentagefault_injured,PrimaFacie_percentagefault_insured,PrimaFacie_percentagefault_otherinsured,PrimaFacie_percentagefault_uninsured,BusinessClass,Perperson_Policylimit,PerOccurrence_PolicyLimit,CombinedSingleLimit, PolicyLimitPerInjury))

```

```{r}
train_num_data = data.frame(
  apply(train_num_data,2,function(x){as.numeric(x)}))

train_cat_data = data.frame(
  apply(train_cat_data,2,function(x){as.factor(x)}))

test_num_data = data.frame(
  apply(test_num_data,2,function(x){as.numeric(x)}))

test_cat_data = data.frame(
  apply(test_cat_data,2,function(x){as.factor(x)}))
```


# scaling numeric data
```{r}
# train_num_data = scale(train_num_data)
# dim(train_num_data)
# str(train_num_data)
# summary(train_num_data)
# 
# test_num_data = scale(test_num_data)
# dim(test_num_data)
# str(test_num_data)
# summary(test_num_data)
```

# tried scaling and the accuracy without scaling seems to be higher that with scaling, so decided to not scale the numeric values

# id and date columns are not adding any significance to the dataset
# so removing id and date columns
```{r}
train_cat_data$ClaimID = NULL
train_cat_data$PolicyID = NULL
train_cat_data$Injury_Date = NULL
train_cat_data$Date_reported = NULL

test_cat_data$ClaimID = NULL
test_cat_data$PolicyID = NULL
test_cat_data$Injury_Date = NULL
test_cat_data$Date_reported = NULL
```

# dummyfying the categorical variables
```{r}
library("dummies")
dim(train_cat_data)
train_cat_data = dummy.data.frame(data = train_cat_data, names = names(test_cat_data))
dim(train_cat_data)

dim(train_cat_data)
test_cat_data = dummy.data.frame(data = test_cat_data, names = names(test_cat_data))
dim(test_cat_data)
```

#combining num and cat data
```{r}
train_data = cbind(train_num_data,train_cat_data)
test_data = cbind(test_num_data,test_cat_data)

dim(train_data)
dim(test_data)
```

```{r}
library(caret)
set.seed(500) 
```

# k cross validation
# cross validation does a train - test split of 80-20 and runs it k times
# k=5

```{r}
#train.control <- trainControl(method = "cv", number = 5)
train.control <- trainControl(method = "repeatedcv", number = 5, repeats = 3)
```

# seed = 500
# accuracy = 0.6338345
# all columns intact = 0.6914080
```{r}
model_logr <- train(ClaimSize ~ .,data=train_data, method = "multinom", trControl = train.control)
print(model_logr)
```

# seed = 673
# accuracy = 0.6251645
```{r}
# Train the model - Decision Tree
model_knn <- train(ClaimSize ~ .,data=train_data, method = "knn", trControl = train.control)
# Summarize the results
print(model_knn)

```

# seed = 673
# accuracy = 0.5035712
```{r}
# Train the model - Naive Bayes
model_nb <- train(ClaimSize ~ .,data=train_data, method = "naive_bayes", trControl = train.control)
# Summarize the results
print(model_nb)
```

# seed = 673
# accuracy = 0.6270352
```{r}
# Train the model - Decision Tree
model_svm <- train(ClaimSize ~ .,data=train_data, method = "lssvmRadial", trControl = train.control)
# Summarize the results
print(model_svm)

```

# seed = 673
# accuracy = 0.6239163
```{r}
# Train the model - Decision Tree
model_svm_linear <- train(ClaimSize ~ .,data=train_data, method = "svmLinear", trControl = train.control)
# Summarize the results
print(model_svm_linear)

```

# seed = 500
# mtry = 6.708204
# ntree = 200
# accuracy = 0.6789208 

# seed = 500
# mtry = 6.708204
# ntree = 500
# accuracy = 0.6777412

# seed = 500
# mtry = 6.708204
# ntree = 400
# accuracy = 0.6776043

# seed = 673
# mtry = 6.708204
# ntree = 400
# accuracy = 0.6784341

# seed = 673
# mtry = 6.708204
# ntree = 200
# accuracy = 0.6786429 


# seed = 673
# mtry = 6.708204
# ntree = 200
# accuracy = 0.7313578
# all features intact


```{r}
# Train the model - Random Forrest
mtry <- c(sqrt(ncol(train_data)))
print(mtry)
tunegrid <- expand.grid(.mtry=mtry)
metric <- "Accuracy"
model_rf_200 <- train(ClaimSize ~ .,data=train_data, ntree = 200, method = "rf", metric=metric, tuneGrid=tunegrid, trControl = train.control)
# Summarize the results
print(model_rf_200)
```

```{r}
# Train the model - Random Forrest
mtry <- c(sqrt(ncol(train_data)))
print(mtry)
tunegrid <- expand.grid(.mtry=mtry)
metric <- "Accuracy"
model_rf <- train(ClaimSize ~ .,data=train_data, ntree = 500, method = "rf", metric=metric, tuneGrid=tunegrid, trControl = train.control)
# Summarize the results
print(model_rf)
```

# seed = 673
# accuracy = 0.6730933


```{r}
# Train the model - XG Boost
metric <- "Accuracy"
# param_grid <- expand.grid(.nrounds = 1000,
#                           .max_depth = c(2, 4, 6, 8, 10),
#                           .eta = c(0.01, 0.001, 0.0001),
#                           .gamma = 1,
#                           .colsample_bytree = c(0.6, 0.4),
#                           .min_child_weight = 1,
#                           .subsample = c(0.6, 0.9))
# model_z_xgbTree <- train(outcome ~ .,data=train, metric=metric, method = "xgbTree", trControl = train.control, tuneGrid = param_grid)
model_xgbTree <- train(ClaimSize ~ .,data=train_data, metric=metric, method = "xgbTree", trControl = train.control)
# Summarize the results
print(model_xgbTree)
```


# log R
# NB
# SVM
# KNN
# RF
#XGB

# comparing results of different models
```{r}
results <- resamples(list(log_r = model_logr, knn = model_knn, nb = model_nb, svm = model_svm, svm_linear = model_svm_linear, rf_200 = model_rf_200, rf = model_rf, xgb = model_xgbTree))
summary(results)
dotplot(results)
```


# predict on train
```{r}
preds_log_r <- predict(model_logr, train_data)
confusionMatrix(data = preds_log_r, reference = train_data$ClaimSize)

preds_nb <- predict(model_nb, train_data)
confusionMatrix(data = preds_nb, reference = train_data$ClaimSize)

preds_knn <- predict(model_knn, train_data)
confusionMatrix(data = preds_knn, reference = train_data$ClaimSize)

preds_svm <- predict(model_svm, train_data)
confusionMatrix(data = preds_svm, reference = train_data$ClaimSize)

preds_rf <- predict(model_rf, train_data)
confusionMatrix(data = preds_rf, reference = train_data$ClaimSize)

preds_xgbTree <- predict(model_xgbTree, train_data)
confusionMatrix(data = preds_xgbTree, reference = train_data$ClaimSize)
```

# predict on test
# individual predictors
```{r}

preds_log_r_test <- predict(model_logr, newdata=test_data)
length(preds_log_r_test)

preds_nb_test <- predict(model_nb, test_data)
length(preds_nb_test)

preds_knn_test <- predict(model_knn, newdata=test_data)
length(preds_knn_test)

preds_svm_test <- predict(model_svm, newdata=test_data)
length(preds_svm_test)

preds_rf_test <- predict(model_rf, newdata=test_data)
length(preds_rf_test)

preds_xbgTree_test <- predict(model_xgbTree, newdata=test_data)
length(preds_xbgTree_test)

```

# log R
# NB
# SVM
# KNN
# RF
#XGB

# create output file
```{r}
test_raw_data = read.csv("Test-1542969243754 (1).csv",header=T,na.strings = c(NA,"?"," ","",".","NA"))

output = data.frame(test_raw_data$ClaimID,preds_rf_test)

names(output)=c('ClaimID','ClaimSize')
dim(output)
str(output)

write.csv(output,file="output_rf.csv",row.names=FALSE)
```











